Re-fit

### 2022-08-17 scripts/r/04_refit/refit_sc.Rmd
♻️ - refit nestor_idahoensis with default priors

Not sure which priors to use after scaling.

```{r}
priors2 = c(
  #weakly informative priors for intercepts and beta for each response variable
  prior(normal(0,1.5), class = Intercept, resp = f0),
  prior(normal(0,1.5), class = b, resp = f0),
  prior(normal(0,1.5), class = Intercept, resp = duration),
  prior(normal(0,1.5), class = b, resp = duration),
  prior(normal(0,1.5), class = Intercept, resp = f15),
  prior(normal(0,1), class = b, resp = f15),
  prior(normal(0,1), class = Intercept, resp = f25),
  prior(normal(0,1), class = b, resp = f25),
  #weakly informative priors for random effects (slopes)
  prior(cauchy(0,0.1), class = sd, group = ID, resp = f0),
  prior(cauchy(0,0.1), class = sd, group = ID, resp = duration),
  prior(cauchy(0,0.1), class = sd, group = ID, resp = f15),
  prior(cauchy(0,0.1), class = sd, group = ID, resp = f25),
  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f0),
  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = duration),
  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f15),
  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f25),
  #weakly informative priors for the correlation between random intercept and slope
  prior(lkj(2), class = cor, group = ID),
  prior(lkj(2), class = cor, group = targetWord),
  prior(cauchy(0, 1), class = sigma, resp=f0),
  prior(cauchy(0, 1), class = sigma, resp=duration),
  prior(cauchy(0, 1), class = sigma, resp=f15),
  prior(cauchy(0, 1), class = sigma, resp=f25)
)

nestor_idahoensis_1_mult_cat <- brm(
  mvbind(f0, duration, f15, f25) ~
    effect_cat +
    (1|ID) + (1|targetWord) +
    (0 + typicality|ID) +
    (0 + typicality|targetWord),
  data = msa_data,
  family = gaussian(),
  prior = priors2, chains = 4, cores = 4,
  threads = threading(2, grainsize = 100),
  backend = "cmdstanr",
  # control = list(max_treedepth = 15, adapt_delta = 0.9),
  file = "./data/analyses/models/nestor_idahoensis_1_mult_cat.rds",
  seed = my_seed
)
```

>>>>

~~Not sure which priors to use after scaling.~~

We have decided to use default (flat) priors.

```{r}
# priors2 = c(
#   #weakly informative priors for intercepts and beta for each response variable
#   prior(normal(0,1.5), class = Intercept, resp = f0),
#   prior(normal(0,1.5), class = b, resp = f0),
#   prior(normal(0,1.5), class = Intercept, resp = duration),
#   prior(normal(0,1.5), class = b, resp = duration),
#   prior(normal(0,1.5), class = Intercept, resp = f15),
#   prior(normal(0,1), class = b, resp = f15),
#   prior(normal(0,1), class = Intercept, resp = f25),
#   prior(normal(0,1), class = b, resp = f25),
#   #weakly informative priors for random effects (slopes)
#   prior(cauchy(0,0.1), class = sd, group = ID, resp = f0),
#   prior(cauchy(0,0.1), class = sd, group = ID, resp = duration),
#   prior(cauchy(0,0.1), class = sd, group = ID, resp = f15),
#   prior(cauchy(0,0.1), class = sd, group = ID, resp = f25),
#   prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f0),
#   prior(cauchy(0,0.1), class = sd, group = targetWord, resp = duration),
#   prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f15),
#   prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f25),
#   #weakly informative priors for the correlation between random intercept and slope
#   prior(lkj(2), class = cor, group = ID),
#   prior(lkj(2), class = cor, group = targetWord),
#   prior(cauchy(0, 1), class = sigma, resp=f0),
#   prior(cauchy(0, 1), class = sigma, resp=duration),
#   prior(cauchy(0, 1), class = sigma, resp=f15),
#   prior(cauchy(0, 1), class = sigma, resp=f25)
# )

nestor_idahoensis_1_mult_cat <- brm(
  mvbind(f0, duration, f15, f25) ~
    effect_cat +
    (1|ID) + (1|targetWord) +
    (0 + typicality|ID) +
    (0 + typicality|targetWord),
  data = msa_data,
  family = gaussian(),
  # prior = priors2,
  chains = 4, cores = 4,
  threads = threading(2, grainsize = 100),
  backend = "cmdstanr",
  # control = list(max_treedepth = 15, adapt_delta = 0.9),
  file = "./data/analyses/models/nestor_idahoensis_1_mult_cat.rds",
  seed = my_seed
)
```

Warning: 6 of 4000 (0.0%) transitions ended with a divergence.
